Word2vec learns effective distance of scientific co-affiliation

### 2020-01-27 paper/current/main.tex
putmobility sentence figure in right place
Adding gravity law section

% for quick author comments 
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.8}
\def\del#1{ {\color{light-gray}{#1}} }
\def\yy#1{ {\color{red}\textbf{yy: #1}} }

@@

% Leiden bibliographic data
	% Basic details
	% How was mobility determined?
	% How were university sizes extracted?
	% Organization information? (count, etc.)
% Manually-identified geographic coordiantes
% Leiden rankings (if using prestige)
%

%% Introduce embedding methodology and approach
% Introduce embedding and why we use it
% How were sentences created (use figure)

%% Gravity Law
% Why use gravity law?
% How were geographic distances calculated?
% How are distnaces calculated within the embedding space

@@

\section{Results}\label{sec:results} %{{{

Let $f_{ij}$ represents the total flux (the number of people who moved) between $i$ and $j$. 
Because we are ignoring the directions, $f_{ij} = f_{ji}$. 
The total flux from or to $i$ can be written as $\mu_{i} = \sum_k f_{ik}$. 
Then the conditional probability $p(j|i)$ is simply
\begin{equation}\label{fig:flux_conditional_prob}
p(j|i) = \frac{f_{ij}}{\mu_i}. 
\end{equation}

>>>>

% for quick author comments 
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.8}
\def\del#1{ {\color{light-gray}{#1}} }
\def\yy#1{ {\color{red}\textbf{yy: #1}} }
\def\dk#1{ {\color{red}\textbf{dk: #1}} }

@@

\subsection{Gravity Law}

We model flow of authors across organizations, $f_{ij}$, using the gravity law. 
the gravity law of mobility loosely derives from the physical law of gravity, whereby the attraction between two objects is a function of their mass and the distance between them.
Given its simplicity and flexibility, this formulation and variants have proven incredibly useful for modeling and predicting many kinds of mobility~\cite{jung2008highwaygravity, curiel2018citygravity, lewer2008immigrationgravity, xia2005measlesgravity, truscott2012epidemicgravity, hong2016busgravity}.
Following the gravity law, the expected flow between two organizations is defined as follows,

\begin{equation}
	\label{eq:gravity_basic}
	f_{ij} = C\frac{m_{i}m_{j}}{f(r_{ij})}
\end{equation}

where $m_{i}$ and $m_{j}$ are the yearly-average size of each organization during the time window, and $f(r_{ij}$ is a function of the distance between the two organizations, chosen as to fit the data, and $C$ is a constant. 
Form this standard formulation we also define what we term the \textit{flux}, or the expected flow between organizations given their size, as a function of distance,

\begin{equation}
	\label{eq:gravity_flux}
	F_{ij} = \frac{f_{ij}}{m_{i}m_{j}} = Cf(r_{ij})
\end{equation}

\dk{We need to mention why we choose these distance functions}

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$. 
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \label{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

\begin{equation}
	\label{eq:linear_flux_geo}
	\ln(F_{ij}) = \ln(C) - \alpha \ln(g_{ij})
\end{equation}

\begin{equation}
	\label{eq:linear_flux_emb}
	\ln(F_{ij}) = \ln(C) + \beta d_{ij}
\end{equation}

The gravity law of mobility is known to be sensitive to the case where $f_{ij} = 0$, or zero movement between organizations. 
Here, non-zero flows account for only 4.2 percent of all possible pairs of  the 6,580 organizations represented in the embedding.
This value is comparable to other common applications of the gravity law, such as to hone calls, commuting, and migration \cite{simini2012universal}.
We follow standard practice and exclude from our analysis zero flows.

@@

\section{Results}\label{sec:results} %{{{ 
Let $f_{ij}$ represents the total flux (the number of people who moved) between $i$ and $j$. 
Because we are ignoring the directions, $f_{ij} = f_{ji}$. 
The total flux from or to $i$ can be written as $\mu_{i} = \sum_k f_{ik}$. 
Then the conditional probability $p(j|i)$ is simply
\begin{equation}\label{fig:flux_conditional_prob}
p(j|i) = \frac{f_{ij}}{\mu_i}. 
\end{equation}
